---
title: "Data Reading"
author: "Nithya Devadoss"
date: "July 1, 2017"
output: 
  html_document: 
    keep_md: yes
keep_md: true
---
#Data Dictionary:
##Beers data file has 2410 observations and 7 columns: 

##Beers.csv: 
###Name: Name of the beer. 
###Beer ID: Unique identiﬁer of the beer
###ABV: Alcohol by volume of the beer. 
###IBU: International Bitterness Units of the beer. 
###Brewery ID: Brewery id associated with the beer. 
###Style: Style of the beer. 
###Ounces: Ounces of beer.

##Breweries data file has 558 Observations and 4 columns

##Breweries.csv: 
###Brew ID: Unique identiﬁer of the brewery. 
###Name: Name of the brewery. 
###City: City where the brewery is located. 
###State: State where the brewery is located.

## Reading Files 
## Added na.strings to convert blanks to NA for easy data cleanup
```{r, Read csv files, echo=TRUE}
library(readr)
Beers <- read.csv("C:/Nithya/MSDS/Term1/6306_Doing_DS/Week7/CaseStudy/Download/Beers.csv",header=T,na.strings="")
Breweries <- read.csv("C:/Nithya/MSDS/Term1/6306_Doing_DS/Week7/CaseStudy/Download/Breweries.csv",header=T,na.strings="")
```
##Sample Beer data and number of observations
## Beers data file has 2410 observations and 7 columns
```{r,sample}
str(Beers)
head(Beers)
```
#Sample Breweries data
## Breweris data file has 558 Observations and 4 columns
```{r,Sample data}
str(Breweries)
head(Breweries)
```